---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summerrband

<!-- badges: start -->
<!-- badges: end -->

`summerrband` plays for you gel-shift data from "tapes" recorded on Cytiva's 
ImageQuant TL. Wherever the data comes from, once it's in a table (`data.frame`), 
this package gives you also a handle on fitting dissociation constants in various
ways.

## Installation

Since this package is not part of [CRAN](https://CRAN.R-project.org), you must 
install and update the development version from [GitHub](https://github.com/) 
with:

``` r
# install.packages("devtools")
devtools::install_github("benjbuch/summerrband")
```

## Showcases

```{r example}
library(summerrband)
```

### A Song on Import-Me

```{r import1, eval=TRUE, include=FALSE}
my_file <- system.file("extdata", "gel_01.txt", package = "summerrband")
```

This is how a raw IQTL file looks like (truncated):

```{r rawdata, echo=FALSE, message=FALSE, warning=FALSE}
data.table::fread(my_file)[, 1:14]
```

This is how the same file will look like after tidy importing. As an extra benefit
of calling `iqtl_view` instead of `iqtl_read`, we'll play a preview alongside:

```{r tidydata}
iqtl_view(my_file)
```

Let's assign some metadata along with the tunes:

```{r import2}
my_data <- iqtl_meta(my_file, meta_data = list(conc = c(2^seq(10, 0), 1),
                                               protein = "protA",
                                               ligand  = "DNA1"))

head(my_data)
```

Of course, there is a batch function (`iqtl_import_all`) too.

### Fitting the Tune and Tuning the Fit

Four lines to sing:

```{r fitting, warning=FALSE}
library(magrittr)  # for the pipe operator

my_data %>% 
  dplyr::filter(band_id == "band_1") %>% 
  dplyr::group_by(protein, ligand) %>% 
  model_cleanly_groupwise(fit_Kd, formula = vol_frac ~ conc, 
                          newdata = data.frame(conc = 10^seq(0, 3, length.out = 100))) %>% 
  model_display(color = ligand) + ggplot2::facet_wrap(ggplot2::vars(protein))
```

```{r}
my_data %>% 
  dplyr::filter(band_id == "band_1") %>% 
  dplyr::group_by(protein, ligand) %>% 
  model_cleanly_groupwise(fit_Kd, formula = vol_frac ~ conc) %>% 
  dplyr::select(tidy) %>% tidyr::unnest(tidy)
```
We can also employ a model that doesn't assume excess of the non-titrated species 
R. So, when we provide its intial (total) concentration `R0` before the equilibrium 
is reached:

```{r}
my_data %>% 
  dplyr::filter(band_id == "band_1") %>% 
  dplyr::group_by(protein, ligand) %>% 
  model_cleanly_groupwise(fit_Kd, formula = vol_frac ~ conc, R0 = 2.0) %>% 
  dplyr::select(tidy) %>% tidyr::unnest(tidy)
```

It is further possible to include a Hill slope if need be and to switch between
differen fitting algorithms in R.
